Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?

### 2017-02-08 cloneoverflow-latex/cloneoverflow.tex
Fixed the size of figures
Update charts.

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,595 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{exp_framework_new}
	\caption{Experimental framework}
	\label{fig:exp_framework}
\end{figure}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{{\small\texttt{https://archive.org/details/stackexchange}}} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: {\small\texttt{https://github.com/AlDanial/cloc}}}.

@@

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 & 670 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs. After classification, we found 670 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}

@@

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects \cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from {\small{\texttt{www.rgagnon.com/javadetails/java-0426.html}}}. Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from {\small{\texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}}}. This code is used in both Stack Overflow and \texttt{aoi} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from {\small{\texttt{zxing}}}, {\small{\texttt{jasper}}}, {\small{\texttt{java.util}}}, {\small{\texttt{javax.servlet}}}, and {\small{\texttt{org.bouncycastle.crypto}}} project.

@@

\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class. An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small{\texttt{@Override}}} methods of {\small{\texttt{mousePressed}}}, and {\small{\texttt{mouseReleased}}}.

\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons. Mainly, they were caused by the effects of code normalisation applied to the source code before detection. However, the original source code were still different enough when we manually classified them. Other causes include {\small{\texttt{finally}}} or {\small{\texttt{try-catch}}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 42 & 23 & 11,549 & 20 & 103 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 110 & 0 & 382 & 178 & 28,642 & 109 & 2,525 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{outdated}
	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}
	\label{fig:outdated}
\end{figure}

@@

	\caption{62 QS outdated online clone pairs. Outdated clones are caused (\textit{C}) by statement modifications, added, deleted (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}

@@

	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{r|l|c|l|c|p{5cm}|r|r|c|c|c}

@@

			1 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjtools/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			2 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjweaver/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			3 & 2513183 & 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			4 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			5 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
			6 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
			7 & 11861598 & 8-Aug-12 & \texttt{eclipse-SDK} & 4.3 & \texttt{WizardDialog.java}  & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
			8 & 22315734 & 11-Mar-14 & \texttt{hadoop} & 1.0.0 & \texttt{WritableComparator.java}  & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
			9 & 801987 & 29-Apr-09 & \texttt{hadoop} & 1.0.0 & \texttt{StringUtils.java}  & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
			10 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			11 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			12 & 14845581 & 13-Feb-13 & \texttt{hadoop} & 1.0.0 & \texttt{JobSubmissionFiles.java}  & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
			13 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapred/../LineRecordReader.java}  & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			14 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapreduce/../LineRecordReader.java}  & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			15 & 15168494 & 24-Feb-14 & \texttt{hibernate} & 4.2.2 & \texttt{ConnectionProviderInitiator.java}  & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
			16 & 24924255 & 24-Jul-14 & \texttt{hibernate} & 4.2.2 & \texttt{Example.java}  & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
			17 & 23520731 & 7-May-14 & \texttt{hibernate} & 4.2.2 & \texttt{SchemaUpdate.java}  & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
			18 & 8257554 & 26-Nov-11 & \texttt{hibernate} & 4.2.2 & \texttt{SettingsFactory.java}  & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
			19 & 23967852 & 31-Apr-14 & \texttt{hibernate} & 4.2.2 & \texttt{SQLServer2005LimitHandler.java}  & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
			20 & 19298607 & 10-Oct-13 & \texttt{hibernate} & 4.2.2 & \texttt{Oracle9iDialect.java} & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
			21 & 10031897 & 5-Apr-12 & \texttt{hibernate} & 4.2.2 & \texttt{AliasToBeanResultTransformer.java} & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
			22 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
			23 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
			24 & 12936580 & 17-Oct-12 & \texttt{jfreechart} & 1.0.13 & \texttt{AbstractXYItemRenderer.java}  & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
			25 & 16058183 & 17-Apr-13 & \texttt{jfreechart} & 1.0.13 & \texttt{KeyToGroupMap.java}  & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
			26 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
			27 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
			28 & 6722760 & 17-Jul-11 & \texttt{jgraph} & 5.13.0.0 & \texttt{HelloWorld.java} (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
			31 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
			32 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
			33 & 23586872 & 31-May-14 & \texttt{junit} & 4.11 & \texttt{Assert.java} & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
			34 & 7504040 & 29-Sep-11 & \texttt{junit} & 4.11 & \texttt{ExternalResource.java}  & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
			35 & 8802082 & 10-Jan-12 & \texttt{junit} & 4.11 & \texttt{ExpectException.java} (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
			37 & 12593810 & 26-Sep-12 & poi & 3.6 & \texttt{WorkbookFactory.java}  & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
			38 & 20913543 & 6-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{AutowireUtils.java} & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
			39 & 18623736 & 4-Sep-13 & \texttt{spring} & 3.0.5  & \texttt{CustomCollectionEditor.java}  & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
			40 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			41 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			42 & 20421869 & 6-Dec-13 & \texttt{spring} & 3.0.5  & \texttt{ClassPathScanningCandidate \newline ComponentProvider.java} (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
			44 & 3751463 & 20-Sep-10 & \texttt{spring} & 3.0.5  & \texttt{ScheduledTasksBean \newline DefinitionParser.java}  & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
			45 & 6149818 & 27-May-11 & \texttt{spring} & 3.0.5  & \texttt{DefaultPropertiesPersister.java}  & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
			46 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{HibernateTemplate.java}  & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
			47 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{Jaxb2Marshaller.java}  & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
			48 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{test/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
			49 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{web/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			50 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{servlet/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\

>>>>

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,632 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://to.be.disclosed.after.review} and can be used as a clone oracle.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{exp_framework_new}
	\caption{Experimental framework}
	\label{fig:exp_framework}
\end{figure}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 75 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 & 668 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs. After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}

@@

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects \cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html. Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/. This code is used in both Stack Overflow and {\small\texttt{aoi}} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and {\small\texttt{org.bouncycastle.crypto}} project.

@@

\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class. An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small\texttt{@Override}} methods of {\small\texttt{mousePressed}}, and {\small\texttt{mouseReleased}}.

\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons. Mainly, they were caused by the effects of code normalisation applied to the source code before detection. However, the original source code were still different enough when we manually classified them. Other causes include {\small\texttt{finally}} or {\small\texttt{try-catch}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 40 & 23 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 110 & 0 & 380 & 178 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{freshness}
	\caption{Freshness of 110 QS online clone pairs}
	\label{fig:outdated}
\end{figure}

@@

	\caption{62 QS outdated online clone pairs. Outdated clones are caused (\textit{C}) by modified/added/deleted statements (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}

@@

	\resizebox{2\columnwidth}{!}{%
	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}

@@

			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
			35 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
			37 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
			38 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
			39 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
			40 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			41 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			42 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
			44 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
			45 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
			46 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
			47 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
			48 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
			49 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			51 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			52 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
			53 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			54 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
			55 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
			56 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
			57 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
